miniKanren with fair search strategies

### 2019-05-07 Paper/paper.tex
grammer checked

A more interesting situation is when the first conjunct produces infinite many 
answers. Consider the following example, a naive specification of fair \conj{} 
might require search strategies to produce all sorts of singleton lists, but no 
longer ones, which makes the strategies incomplete. A search strategy is 
\emph{complete} iff it can find out all the answers in finite time, otherwise, 
it is \emph{imcomplete}.

@@

In this section we review the implementation of interleaving depth-first search 
(\DFSi). This review is for comparison with other search strategies in this 
paper. Thus we focus on parts that are changed later. TRS2 
\citep{friedman_reasoned_2018} provides a comprehensive description of the 
whole miniKanren implementation.

@@

Fig.~\ref{DFSi} shows part of the implementation of \DFSi{}. We follow a
convention to name variables bound to states with `s', to name variables bound 
to goals with `g', and to name variables bound to search spaces with a suffix 
`-inf'. The first function, \texttt{disj2}, implements binary disjunction. 
\texttt{append-inf} is its helper, which compose two disjunctive search spaces. 
The following function, \texttt{conj2}, implements binary conjunction. It applys 
the \emph{first} goal to the input state, then applys the second goal to 
states in the resulting search space. The latter process is done with a helper 
function. \texttt{append-map-inf} applys its input goal to states in its input 
search spaces and compose the resulting search spaces. It reuse 
\texttt{append-inf} for search space composition. The following three 
definitions introduces syntactic sugars that miniKanren users are more familiar 
with. The first two definitions say disjunction and disjunction are 
right-associative. The next and last definition says \conde{} relates its 
clauses disjunctively, and goals in the same clause conjunctively.

>>>>

A more interesting situation is when the first conjunct produces infinite many 
answers. Consider the following example, a naive specification of fair \conj{} 
might require search strategies to produce all sorts of singleton lists, but no 
longer ones, which makes the strategies incomplete. A search strategy is 
\emph{complete} iff it can find out all the answers within finite time, 
otherwise, 
it is \emph{imcomplete}.

@@

In this section, we review the implementation of interleaving depth-first 
search 
(\DFSi). This review is for comparison with other search strategies in this 
paper. Thus we focus on parts that are changed later. TRS2 
\citep{friedman_reasoned_2018} provides a comprehensive description of the 
whole miniKanren implementation.

@@

Fig.~\ref{DFSi} shows part of the implementation of \DFSi{}. We follow a
convention to name variables bound to states with `s', to name variables bound 
to goals with `g', and to name variables bound to search spaces with a suffix 
`-inf'. The first function, \texttt{disj2}, implements binary disjunction. 
\texttt{append-inf} is its helper, which compose two disjunctive search spaces. 
The following function, \texttt{conj2}, implements binary conjunction. It 
applies 
the \emph{first} goal to the input state, then applies the second goal to 
states in the resulting search space. The latter process is done with a helper 
function. \texttt{append-map-inf} applys its input goal to states in its input 
search spaces and compose the resulting search spaces. It reuse 
\texttt{append-inf} for search space composition. The following three 
definitions introduce syntactic sugars that miniKanren users are more familiar 
with. The first two definitions say disjunction and disjunction are 
right-associative. The next and last definition says \conde{} relates its 
clauses disjunctively, and goals in the same clause conjunctively.
